% new tcolorbox environment
\newtcolorbox{topQuark}[2][]{
  coltext      = black,
  colframe     = \MyBlockFrameColorLeft,
  colback      = \MyBlockFillColorLeft,
  colbacktitle = \MyBlockTitleBoxColor,
  coltitle     = black,
  title        = {\Large{\textbf{#2}}},
  fonttitle    = \bfseries,
  boxrule      = 0.2cm, %frame line width
  %tikz={rotate=#3}, % manipulate the tcolorbox as a whole (in degrees)
  top=+0.0cm, bottom=+0.0cm, left=+0.05cm, right=+0.05cm,
  %enlarge top by   = +1.0cm,  %  equivalent to mdframed 'skipabove'
  %enlarge bottom by= +0.0cm,  %  equivalent to mdframed 'skipbelow'
  %enlarge left by  = +1.5cm,  
  %enlarge right by = +0.0cm, 
  opacityback=1.0, % 1.0 means totally transparent, 0.0 means totally opaque
  arc=0.0cm,        % 0.0cm for non-rounded corners!
  #1,
}

% https://arxiv.org/abs/0710.1895
\begin{topQuark}[enhanced, tikz={rotate=0}]{Measurement of correlated
    $b\bar{b}$ production}
  \begin{multicols}{2}
    We present a measurement of the correlated $b\bar{b}$ production cross
    section. The data used in this analysis were taken with the upgraded
    CDF detector (CDF II) at the Fermilab Tevatron collider, and
    correspond to an integrated luminosity of 742 pb−1. We utilize muon
    pairs with invariant mass $5 \leq m_{\mu\mu} \leq 80 \gevcc$
    produced by bb¯ double semileptonic decays. For muons with
    $p_T \geq 3 \gevc$ and $|\eta| \le $0.7, that are produced by $b$
    and $\bar{b}$ quarks with $p_T \geq 2 \gevc$ and $|y|\le$1.3, we
    measure $\sigma_{b\rightarrow \mu, \bar{b} \rightarrow
      \mu}$=1549$\pm$133 $pb$.
    We compare this result with theoretical predictions and previous
    measurements.
    We also report the measurement of $\sigma_{c\rightarrow \mu, \bar{c}\rightarrow \mu}$, a by-product of the study of the background to $b\bar{b}$ production.  
  \end{multicols}
\end{topQuark}

\begin{topQuark}[enhanced, tikz={rotate=0}]{Measurement of correlated $b\bar{b}$ production with first CMS data!}
  \begin{multicols}{2}
    A measurement of the inclusive cross section for the process pp to b b-bar X to muon muon X' at $\sqrt{s}$ = 7 TeV is presented, based on a data sample corresponding to an integrated luminosity of 27.9 inverse picobarns collected by the CMS experiment at the LHC. By selecting pairs of muons each with pseudorapidity $\abs{eta}$<2.1, the value of the cross section for pp to b b-bar X to muon muon X' is found to be 26.4 +/- 0.1 (stat.) +/- 2.4 (syst.) +/- 1.1 (lumi.) nb is obtained for muons with transverse momentum greater than 4 GeV, and 5.12 +/- 0.03 (stat.) +/- 0.48 (syst.) +/- 0.20 (lumi.) nb for transverse momenta greater than 6 GeV. These results are compared to QCD predictions at leading and next-to-leading orders.
  \end{multicols}
\end{topQuark}
