 \begin{thebibliography}{99}
 \label{bibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Introduction
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibitem{ewgroup} The ALEPH,  DELPHI, L3, and OPAL Collaborations and the LEP
                  Electroweak Working Group, {\it A Combination of preliminary
                  electroweak measurements and constraints on the standard
                  model}, arXiv:hep-ex/0612034.
\bibitem{hlim}    The ALEPH,  DELPHI, L3, and OPAL Collaborations,
                  Phys.~Lett.~B~{\bf 565}, 61 (2003).
\bibitem{gunion}  R.~Dermisek and J.~F.~Gunion, Phys.~Rev.~D~{\bf 76}, 095006
                  (2007).
\bibitem{fullana} E.~Fullana {\it et al.}, Phys.~Lett.~B~{\bf 563}, 67 (2007).
\bibitem{gunion1} S.~Chang {\it et al.}, arXiv:0801.455v2.
\bibitem{hidval}  M.~J.~Stressler {\it et al.}, Phys.~Lett.~B~{\bf 651}, 374
                  (2007).
\bibitem{bbxs}    T.~Aaltonen {\it et al.,} Phys.~Rev.~D {\bf 77}, 072004 (2008).
\bibitem{a0disc}  T.~Aaltonen {\it et al.,} arXiv:0810.5357.
\bibitem{ip}      The impact parameter is the distance of closest approach of
                  a track to the primary event vertex in the plane transverse 
                    to the beam direction.
\bibitem{pythia}  T.~Sj\"{o}strand and M.~Bengtsson, 
                  Comp.~Phys.~Commun.~{\bf 43}, 367 (1987);
                  H.~Bengtsson and T.~Sj\"{o}strand,
                  Comp.~Phys.~Commun.~{\bf 46}, 43 (1987);
                  T.~Sj\"{o}strand {\it et al.,} Comp.~Phys.~Commun.~{\bf 135},
                  238 (2001).
\bibitem{sim}     We have generated several simulated samples with a Higgs
                  mass, $m_H$, ranging from 115 to 300 $\gevcc$ using the 
                  option {\sc isub=151} of the version 6.4 of the {\sc pythia}
                  Monte Carlo program. We have also generated pair production
                  of Higgs bosons ($f\bar{f} \rightarrow h_n h_n$) with the
                  option {\sc isub=300}. The $h_n$ widths are set to be negligible
                  with respect to the detector resolution. 
                   We use the interface {\sc pyslha.f}
                  and decay Higgs bosons according to phase space. The $\tau$
                  decays are simulated with the {\sc tauola}
                  program~\cite{tauola} 
\bibitem{tauola}  S.~Jadach {\it et al.,} Comp.~Phys.~Commun.~{\bf 76}, 361
                  (1993). We use {\sc tauola} Library version {\sc 2.6}.
\bibitem{sim1}    In a different simulation, that uses the process
                  $p\bar{p} \rightarrow H \rightarrow h_1 h_1$ with 
                  $m_H =300 \; \gevcc$, this ratio is a factor of two higher
                  than in the data because heavy resonant states are decayed
                  by the {\sc pythia} generator program into $h_1$ pairs with
                  well balanced transverse momenta.
%\bibitem{pdg}    W.-M.~Yao {\it et al.,} J.~Phys.~G~{\bf 33}, 1 (2006).

\end{thebibliography}








